Discriminative Sensing Based on Signal Processing

### 2017-10-17 docs/thesis/chapters/3_eigen_similarity/eigen_similarity.tex
compiling version

\begin{figure}[h!]
     \centering 
     \includegraphics[height=6cm, width=9cm]{results/figures/fig09.png}
     \caption{Scenario to reproduce legitimate traffic, noise, flood and port scan.}
     \label{fig:fig1}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=4.5cm, width=9cm]{results/figures/fig03.png}
     \caption{Traffic from user's operations, that can be characterized by web access, traffic of well-known applications or network protocols.}
     \label{fig:fig3}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=4.5cm, width=9cm]{results/figures/fig04.png}
     \caption{Network traffic of user independent operations for network management.}
     \label{fig:fig4}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=4.5cm, width=9cm]{results/figures/fig05.png}
     \caption{A large quantity of SYN requests to a target, in order to cause a DoS.}
     \label{fig:fig5}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=4.5cm, width=9cm]{results/figures/fig06.png}
     \caption{Large amount of “UDP echo” requests and replies, causing packet flooding.}
     \label{fig:fig6}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=5cm, width=9cm]{results/figures/fig07.png}
     \caption{Connection attempts in order to identify active ports.}
     \label{fig:fig7}
\end{figure}

@@

\begin{figure}[h!]
	\centering
     \includegraphics[height=11cm, width=9cm]{results/figures/mos_eigen_similarity.eps}
     \caption{Overview of The Framework for Detection and Identification of Network Attacks.}
     \label{fig:fig80}
\end{figure}

@@

\begin{figure}[h!]
     \includegraphics[height=4cm, width=12.4cm]{results/figures/incremental.eps}
     \caption{Traffic selection for incremental approach.}
     \label{fig:fig8}
\end{figure}

@@

\begin{figure}[h!]
     \includegraphics[height=4cm, width=12.4cm]{results/figures/individualized.eps}
     \caption{Traffic selection for individual approach.}
     \label{fig:fig9}
\end{figure}

@@

\begin{figure}[h!]
     \includegraphics[height=4cm, width=12.4cm]{results/figures/incremental_individualized.eps}
     \caption{Traffic selection for incremental individualized approach.}
     \label{fig:fig2}
\end{figure}

@@

\begin{figure}[h!]
	\centering
     \includegraphics[height=6cm, width=8cm]{results/figures/eigenvalues_synflood.eps} 
     \caption{Eigenvalues of the sample covariance matrix (synflood).}
     \label{fig:fig10}
\end{figure}

@@

\begin{figure}[h!]
	\centering
     \includegraphics[height=6cm, width=8cm]{results/figures/eigenvalues_fraggle.eps}
     \caption{Eigenvalues of the sample covariance matrix (fraggle).}
     \label{fig:fig11}
\end{figure}

@@

\begin{figure}[h!]
	\centering
     \includegraphics[height=6cm, width=8cm]{results/figures/eigenvalues_portscan.eps}
     \caption{Eigenvalues of the covariance matrix of zero mean and unitary standard deviation (port scan).}
     \label{fig:fig12}
\end{figure}

>>>>

\begin{figure}[h!]
     \centering 
     \includegraphics[height=6cm, width=9cm]{figures/fig09.png}
     \caption{Scenario to reproduce legitimate traffic, noise, flood and port scan.}
     \label{fig:fig1}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=4.5cm, width=9cm]{figures/fig03.png}
     \caption{Traffic from user's operations, that can be characterized by web access, traffic of well-known applications or network protocols.}
     \label{fig:fig3}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=4.5cm, width=9cm]{figures/fig04.png}
     \caption{Network traffic of user independent operations for network management.}
     \label{fig:fig4}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=4.5cm, width=9cm]{figures/fig05.png}
     \caption{A large quantity of SYN requests to a target, in order to cause a DoS.}
     \label{fig:fig5}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=4.5cm, width=9cm]{figures/fig06.png}
     \caption{Large amount of “UDP echo” requests and replies, causing packet flooding.}
     \label{fig:fig6}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=5cm, width=9cm]{figures/fig07.png}
     \caption{Connection attempts in order to identify active ports.}
     \label{fig:fig7}
\end{figure}

@@

\begin{figure}[h!]
	\centering
     \includegraphics[height=11cm, width=9cm]{figures/mos_eigen_similarity.eps}
     \caption{Overview of The Framework for Detection and Identification of Network Attacks.}
     \label{fig:fig80}
\end{figure}

@@

\begin{figure}[h!]
     \includegraphics[height=4cm, width=12.4cm]{figures/incremental.eps}
     \caption{Traffic selection for incremental approach.}
     \label{fig:fig8}
\end{figure}

@@

\begin{figure}[h!]
     \includegraphics[height=4cm, width=12.4cm]{figures/individualized.eps}
     \caption{Traffic selection for individual approach.}
     \label{fig:fig9}
\end{figure}

@@

\begin{figure}[h!]
     \includegraphics[height=4cm, width=12.4cm]{figures/incremental_individualized.eps}
     \caption{Traffic selection for incremental individualized approach.}
     \label{fig:fig2}
\end{figure}

@@

\begin{figure}[h!]
	\centering
     \includegraphics[height=6cm, width=8cm]{figures/eigenvalues_synflood.eps} 
     \caption{Eigenvalues of the sample covariance matrix (synflood).}
     \label{fig:fig10}
\end{figure}

@@

\begin{figure}[h!]
	\centering
     \includegraphics[height=6cm, width=8cm]{figures/eigenvalues_fraggle.eps}
     \caption{Eigenvalues of the sample covariance matrix (fraggle).}
     \label{fig:fig11}
\end{figure}

@@

\begin{figure}[h!]
	\centering
     \includegraphics[height=6cm, width=8cm]{figures/eigenvalues_portscan.eps}
     \caption{Eigenvalues of the covariance matrix of zero mean and unitary standard deviation (port scan).}
     \label{fig:fig12}
\end{figure}
